Hydras \& Co.

### 2022-11-14 doc/chapter-fol.tex

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.Ackermann.LNN.html}{Ackermann.LNN\_Examples}

>>>>

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.Ackermann.LNN.html}{Ackermann.LNN}
